Technique for \earlywarning\ detection of compact binary coalescence and its implication for multi-messenger astronomy

### 2011-06-03 introduction.tex
rearrange detector references fix typo
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@903 ccdd05d5-56c1-461a-bf98-85f6876523b4

\editorial{Would the introduction be more effective without this paragraph?}
The coalescence of compact binary systems consisting of neutron stars (NS)
and/or black holes (BH) is the most promising source of gravitational radiation
for Advanced \LIGO~\cite{ALIGOWeb}, Virgo~\cite{AVirgoWeb}, \GEO~\cite{GEOWeb},%
\editorial{Can we condense all of the detector citations into one -- perhaps find a whitepaper?}%
and \LCGT~\cite{LCGTWeb}.  Tens of binary coalescence events are expected to be
observed in the advanced detector era later this
decade~\cite{Abadie:2010p10836}.

@@

Advance detection of compact binary coalescences (\CBC{}s) will require striking a balance between latency
and throughput.  \CBC{} searches consist of banks of matched filters, or
cross-correlations between the data stream and a bank of nominal ``template''
signals.  There are many different implementations of matched filters, but most
have high throughput at the cost of high latency, or low latency at the cost of
low throughput.  The former are epitomized by the overlap-save algorithm for
\textsc{fft} convolution, currently the preferred method in gravitational wave
searches.  The most obvious example of the latter is the time domain
(\textsc{td}) convolution, which is has no latency at all.  However, its
computational complexity is quadratic in the length of the templates, so it is
prohibitively expensive for long templates.

>>>>

\editorial{Would the introduction be more effective without this paragraph?, should we find whitepapers?}

The coalescence of compact binary systems consisting of neutron stars (NS)
and/or black holes (BH) is the most promising source of gravitational radiation
for Advanced \LIGO, Virgo, \GEO\ and \LCGT~\cite{ALIGOWeb, AVirgoWeb, GEOWeb,
LCGTWeb}.  Tens of binary coalescence events are expected to be observed in the
advanced detector era later this decade~\cite{Abadie:2010p10836}.

@@

Advance detection of compact binary coalescences (\CBC{}s) will require striking a balance between latency
and throughput.  \CBC{} searches consist of banks of matched filters, or
cross-correlations between the data stream and a bank of nominal ``template''
signals.  There are many different implementations of matched filters, but most
have high throughput at the cost of high latency, or low latency at the cost of
low throughput.  The former are epitomized by the overlap-save algorithm for
\textsc{fft} convolution, currently the preferred method in gravitational wave
searches.  The most obvious example of the latter is the time domain
(\textsc{td}) convolution, which has no latency at all.  However, its
computational complexity is quadratic in the length of the templates, so it is
prohibitively expensive for long templates.
